### 2018-10-01 ms.tex
More messing with fig placement.

@@

\begin{figure}[!t]
% to be removed before submission
\includegraphics[width = 0.7\textwidth]{figures/idn_both_cv12_preds.png}
\caption{{\bf Input incidence data and predicted incidence maps. } 
The incidence (log10) data (top), predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia. The values plotted for areas with no polygon data are the means across all cross-validation folds.
}
\label{predobsmapidn}
\end{figure}

\begin{figure}[!t]
% to be removed before submission
\includegraphics[width = 0.7\textwidth]{figures/sen_both_cv12_preds.png}
\caption{{\bf Input incidence data and predicted incidence maps. } 
The incidence (log10) data, predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for PseudoSenegal.
}
\label{predobsmapsen}
\end{figure}

%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
\begin{figure}[!t]
% to be removed before submission
\includegraphics[width = 1.05\textwidth]{figures/random_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
\caption{{\bf Observed-predicted plots for random cross-validation experiments.}
A-B) Indonesia, C-D) PseudoSenegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
The bimodal distribution in observed prevalence in Indonesia is caused by the large number of surveys with exactly one positive case.
}
\label{randompredobsscatter}
\end{figure}

%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
\begin{figure}[!t]
% to be removed before submission
\includegraphics[width = 1.05\textwidth]{figures/spatial_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
\caption{{\bf Observed-predicted plots for spatial cross-validation experiments.}
A-B) Indonesia, C-D) PseudoSenegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
The bimodal distribution in observed prevalence in Indonesia is caused by the large number of surveys with exactly one positive case.
}
\label{spatialpredobsscatter}
\end{figure}

@@

\begin{table}[!t]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of coverage of 80\% credible intervals.}}
\begin{tabular}{llllll}
\hline
{\bf Holdout data} & {\bf Cross-validation} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
\thickhline 
Incidence & Random & Indonesia & 0.13 & 0.72 &  0.73\\
&& PseudoSenegal & 0.11 & 0.80 &  0.85\\
&& Madagascar & 0.59 & 0.82 &  0.77\vspace{1mm}\\
& Spatial & Indonesia & 0.14 & 0.76 &  0.68\\
&& PseudoSenegal & 0.30 & 0.67 &  0.70\\
&& Madagascar & 0.68 & 0.65 &  0.68\vspace{3mm} \\
Prevalence & Random & Indonesia & 0.90 & 0.50 &  0.80\\
&& PseudoSenegal & 0.80 & 0.71 &  0.91\\
&& Madagascar & 0.83 & 0.53 &  0.74\vspace{1mm}\\
& Spatial & Indonesia & 0.87 & 0.62 &  0.96\\
&& PseudoSenegal & 0.90 & 0.88 &  0.79\\
&& Madagascar & 0.93 & 0.68 &  0.83\\
\end{tabular}
\begin{flushleft}

@@

We have compared the predictive performance of a polygon-only model and a model that jointly learns from polygon incidence data and prevalence point-surveys.
We found that neither model was clearly superior to the other but that both models recovered the broad spatial pattern of malaria risk (Figures \ref{predobsmapidn} and \ref{predobsmapidn}).
With regards to a random cross-validation scheme, adding prevalence point-surveys to the disaggregation model only improved performance in  Madagascar (Table~\ref{table1}).
With regards to a spatial cross-validation scheme, which tests a models ability to predict malaria risk far away from available data, we found that adding the prevalence point-surveys improved on the polygon-only models in both PseudoSenegal and Madagascar but not Indonesia (Table~\ref{table2}).

>>>>

%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
\begin{figure}
% to be removed before submission
\includegraphics[width = 1.05\textwidth]{figures/random_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
\caption{{\bf Observed-predicted plots for random cross-validation experiments.}
A-B) Indonesia, C-D) PseudoSenegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
The bimodal distribution in observed prevalence in Indonesia is caused by the large number of surveys with exactly one positive case.
}
\label{randompredobsscatter}
\end{figure}

%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
\begin{figure}
% to be removed before submission
\includegraphics[width = 1.05\textwidth]{figures/spatial_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
\caption{{\bf Observed-predicted plots for spatial cross-validation experiments.}
A-B) Indonesia, C-D) PseudoSenegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
The bimodal distribution in observed prevalence in Indonesia is caused by the large number of surveys with exactly one positive case.
}
\label{spatialpredobsscatter}
\end{figure}

\begin{table}[t]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of coverage of 80\% credible intervals.}}
\begin{tabular}{llllll}
\hline
{\bf Holdout data} & {\bf Cross-validation} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
\thickhline 
Incidence & Random & Indonesia & 0.13 & 0.72 &  0.73\\
&& PseudoSenegal & 0.11 & 0.80 &  0.85\\
&& Madagascar & 0.59 & 0.82 &  0.77\vspace{1mm}\\
& Spatial & Indonesia & 0.14 & 0.76 &  0.68\\
&& PseudoSenegal & 0.30 & 0.67 &  0.70\\
&& Madagascar & 0.68 & 0.65 &  0.68\vspace{3mm} \\
Prevalence & Random & Indonesia & 0.90 & 0.50 &  0.80\\
&& PseudoSenegal & 0.80 & 0.71 &  0.91\\
&& Madagascar & 0.83 & 0.53 &  0.74\vspace{1mm}\\
& Spatial & Indonesia & 0.87 & 0.62 &  0.96\\
&& PseudoSenegal & 0.90 & 0.88 &  0.79\\
&& Madagascar & 0.93 & 0.68 &  0.83\\
\end{tabular}
\begin{flushleft}

@@

@@

\begin{figure}
% to be removed before submission
\includegraphics[width = 0.7\textwidth]{figures/idn_both_cv12_preds.png}
\caption{{\bf Input incidence data and predicted incidence maps. } 
The incidence (log10) data (top), predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia. The values plotted for areas with no polygon data are the means across all cross-validation folds.
}
\label{predobsmapidn}
\end{figure}

\begin{figure}
% to be removed before submission
\includegraphics[width = 0.7\textwidth]{figures/sen_both_cv12_preds.png}
\caption{{\bf Input incidence data and predicted incidence maps. } 
The incidence (log10) data, predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for PseudoSenegal.
}
\label{predobsmapsen}
\end{figure}

@@

We have compared the predictive performance of a polygon-only model and a model that jointly learns from polygon incidence data and prevalence point-surveys.
We found that neither model was clearly superior to the other but that both models recovered the broad spatial pattern of malaria risk (Figures \ref{predobsmapidn} and \ref{predobsmapsen}).
With regards to a random cross-validation scheme, adding prevalence point-surveys to the disaggregation model only improved performance in  Madagascar (Table~\ref{table1}).
With regards to a spatial cross-validation scheme, which tests a models ability to predict malaria risk far away from available data, we found that adding the prevalence point-surveys improved on the polygon-only models in both PseudoSenegal and Madagascar but not Indonesia (Table~\ref{table2}).
